Blocking-resistant communication through high-value web services

### 2014-05-13 docs/meek.tex
Fix figure label.
traffic characteristics figures

\documentclass{article}  
\usepackage{graphicx}
\usepackage{url}
\usepackage{hyperref}

@@

\begin{figure}
\includegraphics[width=\linewidth]{architecture}
\caption{
System architecture.
The Google frontend server is the server that dispatches requests to different services depending on the Host header.
Components that are new in our system are outlined in blue.
The ``Google infrastructure'' block may be replaced by other infrastructure that supports domain fronting.
}
\label{fig:architecture}
\end{figure}

@@

@@

@@

\begin{figure}
\includegraphics[width=\linewidth]{clients-meek}
\caption{Number of concurrent users using the meek transport,
as reported by the Tor Metrics Portal.
The gap between April~14 and April~22 is when the Tor bridge authority
was down because of the Heartbleed OpenSSL vulnerability~\cite{heartbleed}, and wasn't collecting statistics.}
\label{fig:clients}
\end{figure}

>>>>

\documentclass{article}  
\usepackage{graphicx}
\usepackage{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}

@@

@@

The censor cannot sniff the content of communications or infer the existence of meek traffic 
from packet \emph{data}, 
since the communication is encrypted inside the TLS session, and we have devoted large efforts 
in hiding TLS handshake fingerprints. However, it is still possible that the censor can detect 
the existence of meek traffic according to the \emph{metadata}, i.e. traffic characteristics. 
We studied a collection of traffic characteristics and evaluated their possibilities of becoming
the censor's interest. Specifically, we considered three characteristics: 1) payload length of
TCP packets, 2) number of concurrent HTTPS connections, 3) HTTPS connection lifetime. To collect 
the traffic trace of meek, we browsed the Alexa top 500 websites sequentially using the Tor Browser Bundle
and dumped the traffic trace from 
the network interface. We ensured only the browser can successfully access the network by setting
up the \texttt{iptables} firewall so that packets from other processes will be dropped. We also 
obtained a 10-minute sample of normal HTTPS traffic trace from LBL. The trace is 983 MB in total. We also
specifically extracted the traffic between LBL and Google. Since the trace only has packet headers, we 
cannot extract the domain information. However, the \texttt{TXT} DNS records of the domain 
\texttt{\_netblocks.google.com} shows the IP address blocks that belongs to Google. Therefore, we 
determine whether a flow is from or to Google by examining the address in the IP header. For this
study we are only interested in Google traffic, because the censor will be mostly likely to compare
suspected meek traffic with normal Google traffic. This part of the trace is 312 MB in size.

@@

\begin{figure}
\centering
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[width=\textwidth]{figs/datalen-google-cdf.png}
\caption{Normal Google Traffic}
\label{fig:len:lbl}
\end{subfigure}%
%add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
%(or a blank line to force the subfigure onto a new line)
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[width=\textwidth]{figs/datalen-tbb-cdf.png}
\caption{Traffic Using meek}
\label{fig:len:meek}
\end{subfigure}

\caption{TCP packet payload size distribution}
\label{fig:len}
\end{figure}

\paragraph{TCP payload length}
Figure \ref{fig:len} shows the payload size distribution of normal Google traffic and meek traffic. Both
figures exhibit a significant amount of packets with no payload. Most likely these packets are TCP SYN and ACK
packets. Figure \ref{fig:len:lbl} is the distribution of normal traffic, which indicates a large portion
of small-sized packets. While in the distribution of meek traffic shown in Figure \ref{fig:len:meek}, most packets
are large packets ranging from 1400B to 1500B.

Recall that we use browsers to handle HTTPS connections for meek in order to hide TLS handshake characteristics.
Browsers also apply techniques like HTTP pipelining to improve performance. Since meek is always communicating with
the same Google frontend server, the browser will keep the persistant TLS connection. In addition, small requests 
can be batched into a large chunk before being sent. This explains why large packets are mostly seen from the meek trace.
In contract, normal users may not have persistent connections to Google. For example, a user may search a keyword on
Google, click a result, and then close the tab that displays search results. The browser may close the 
connection immediately after the user leaves the Google web page. Next time the user browses Google search, the browser 
opens a new connection. In this case, small requests do not have such opportunity for batching.

These browser techniques improve performance, but also lead to unexpected results. The censor may be aware of the 
deviation from the distribution of normal traffic. Additionally, the persistent connection itself can be a problem.
We thus investigated other related characteristics.

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth, angle=270]{figs/connections-google.eps}
\caption{Histogram of each user's connections in the 10-minute window}
\label{fig:connections}
\end{figure}
%add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
%(or a blank line to force the subfigure onto a new line)
\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figs/conns.eps}
\caption{Concurrent HTTPS connections over time. We measure the trace for the Tor Browser Bundle and Firefox/Chrome extensions.}
\label{fig:len:meek}
\end{figure}

\paragraph{Concurrent connections}

\begin{figure}
\centering
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[height=\textwidth, angle=270]{figs/flowduration-google-cdf.eps}
\caption{Normal Google Traffic}
\label{fig:len:lbl}
\end{subfigure}%
%add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
%(or a blank line to force the subfigure onto a new line)
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[height=\textwidth, angle=270]{figs/flowduration-tbb-cdf.eps}
\caption{Traffic Using meek}
\label{fig:len:meek}
\end{subfigure}

\caption{Connection lifetime distribution}
\label{fig:len}
\end{figure}

\paragraph{Connection lifetime}

\paragraph{Conclusion}

@@

\begin{figure}
\includegraphics[width=\linewidth]{clients-meek}
\caption{Number of concurrent users using the meek transport,
as reported by the Tor Metrics Portal.
Missing parts of the graph are caused by missing data at the metrics portal.
}
\label{fig:clients}
\end{figure}
